\begin{enumerate}
The following user tasks are intended to exemplify the uses of the system and the different types of users who might find the system useful. The tasks were derived from our user interviews.1. Mrs. Anderson, a middle school English teacher for over 30 years, has a completed lesson plan that has proven to work well over time which involves acting out a scene in a play her class is reading. She has decided that she would like to share this lesson with others so that they may make use of her experiences,information, and plans.  She's familiar with paper teaching boxes in her school, and has only begun using a computer within the last year.2. Mr. Multon is a second grade physical science teacher for an elementary school. He has a lesson for an ``earthquakes'' unit, but needs to plan an activity to accompany it.  He also has an abundance of play-doh at his disposal.3. Ms. Frizzle just started teaching science this year to high schoolers, and recently taught a lesson she obtained from another teacher. She found some issues with teaching it.  For example, sometimes the chemicals that were called for had unusual reactions, and the classroom needed to be evacuated because of the fumes.  She would like to make notes on the lesson about her findings for next time.4. Mr. Johnson teaches Spanish to advanced high school students, and has done so for five years. He is planning a lesson on food names to be taught the following week. He has already assembled much of the information he needs, and feels comfortable with his plan.  Two days later he gets a worksheet from a fellow teacher on ordering at a restaurant that he thinks would add to his lesson very nicely. He wants to incorporate it into his plan.5. George works for the Department of Education and is developing a new content standard to be taught at the 5th grade level. He wants to design a sample lesson demonstrating how the standard could be fulfilled, and provide it to school districts to use.
\end{enumerate}

